\begin{thebibliography}{9}

\bibitem{glasser1993}
GLASSER O., \textit{Wilhelm Conrad Röntgen and the Early History of the Roentgen Rays} [online]. San Francisco: Norman Publishing, 1993. [Accessed 27 April 2020]. ISBN 0-930405-22-6. Available from: https://books.google.sk/books?id=5GJs4tyb7wEC

\bibitem{bhattacharyya2016}
BHATTACHARYAA K. B., Godfrey Newbold Hounsfield (1919–2004): The man who revolutionized neuroimaging. \textit{Ann Indian Acad Neurol.} [online]. October-December 2016, 19(4), pp. 448-450. [Accessed 27 April 2020]. ISSN 1998-3549. Available from: doi:10.4103/0972-2327.194414

\bibitem{lauterbur1973}
LAUTERBUR P.C., Image Formation by Induced Local Interactions: Examples Employing Nuclear Magnetic Resonance. \textit{Nature} [online]. March 1973, 242, pp. 190-191. [Accessed 27 April 2020]. ISSN 1476-4687. Available from: https://www.biac.duke.edu/education/courses/fall05/fmri/readings/
week3/1973\_Nature\_Lauterbur.pdf

\bibitem{eurostat2019}
Medical technologies - examinations by medical imaging techniques (CT, MRI and PET). In: \textit{EUROSTAT} [online]. European Union 2019. [Accessed 27 April 2020]. Available from: https://ec.europa.eu/eurostat/web/products-datasets/-/hlth\_co\_exam

\bibitem{wells2016}
WELLS W.M., Medical Image Analysis – past, present, and future. \textit{Medical Image Analysis} [online]. October 2016, 33, pp. 4-6. [Accessed 27 April 2020]. ISSN 1361-8415. Available from: doi: doi.org/10.1016/j.media.2016.06.013

\bibitem{thresholding}
SAHOO P.K., SOLTANI S., WONG A.K.C, A survey of thresholding technique. \textit{Computer Vision, Graphics, and Image Processing} [online]. 1988, 41(2), pp. 223-260. [Accessed 7 May 2020]. ISSN 0734-189X. Available from: http://www.sciencedirect.com/science/article/pii/0734189X8890022

\bibitem{medical-imaging-handbook}
BANKMAN I.N., \textit{Handbook of Medical Image Processing and Analysis}. London: Academic Press, 2000 ISBN 0-12-077790-8. 

\bibitem{otzu1979}
OTZU N., A Threshold Selection Method from Gray-Level Histograms. \textit{IEEE Transactions on Systems, Man, and Cybernetics} [online]. 1979, 9(1), pp. 62-66. [Accessed 30 April 2020]. ISSN 2168-2909. Available from: doi: 10.1109/TSMC.1979.4310076

\bibitem{clustering}
JAIN A.K., DUBES R.C., \textit{Algorithms for clustering data} [online]. Englewood Cliffs: Prentice-Hall, Inc., 1988. [Accessed 7 May 2020]. ISBN 978-0-13-022278-7. Available from: https://homepages.inf.ed.ac.uk/rbf/BOOKS/JAIN/Clustering\_Jain\_Dubes.pdf


\bibitem{macqueen1967}
MACQUEEN J., Some methods for classification and analysis of multivariate observations. In: \textit{Proceedings of the Fifth Berkeley Symposium on Mathematical Statistics and Probability} [online]. Berkley: University of California Press, 1967. [Accessed 7 May 2020]. Available from: https://projecteuclid.org/euclid.bsmsp/1200512992

\bibitem{ng2006}
NH H.P., ONG S.H., FOONG K., GOH P.M., NOWINSKY W.L. Medical Image Segmentation Using K-Means Clustering and Improved Watershed Algorithm. In: \textit{IEEE Southwest Symposium on Image Analysis and Interpretation} [online]. Denver: IEEE, 2006. [Accessed 7 May 2020]. Available from: doi: 10.1109/SSIAI.2006.1633722

\bibitem{bezdek1981}
BEZDEK J.C., \textit{Pattern Recognition with Fuzzy Objective Function Algorithms} [online]. Boston: Springer, 1981. [Accessed 7 May 2020]. ISBN 978-1-4757-0450-1.
Available from: https://www.researchgate.net/publication/233932672\_Pattern
\_Recognition\_With\_Fuzzy\_Objective\_Function\_Algorithms

\bibitem{barrett-keat2004}
BARRETT J.F., KEAT N., Artifacts in CT: Recognition and Avoidance. \textit{RadioGraphics} [online]. November 2004, 24(6). [Accessed 30 April 2020]. ISSN 1527-1323. Available from: doi: doi.org/10.1148/rg.246045065

\bibitem{goldman2007}
GOLDMAN L.W., Principles of CT and CT Technology. In: \textit{Journal of Nuclear Medicine Technology} [online]. September 2007, 35(3), p.115-128. [Accessed 3 May 2020]. ISSN 1535-5675. Available from: doi:10.2967/jnmt.107.042978


\bibitem{neuro2016}
LI X. et al. The first step for neuroimaging data analysis: DICOM to NIfTI conversion. \textit{Journal of Neuroscience Methods} [online]. 2006, 264. [Accessed 19 April 2020]. ISSN 1872-678X. Available from: doi: doi.org/10.1016/j.jneumeth.2016.03.001

\bibitem{DICOM-spec}
\textit{DICOM PS3.1 2020b - Introduction and Overview} [online]. NEMA. [Accessed 30 April 2020]. Available from: http://dicom.nema.org/medical/dicom/current/output/pdf/part01.pd

\bibitem{nifti}
\textit{Neuroimaging Informatics Technology Initiative} [online]. NIMH. [Accessed 30 April 2020]. Available from: https://nifti.nimh.nih.gov

\bibitem{coordinate-systems}
\textit{Coordinate systems and affines} [online]. NiBabel. [Accessed 7 May 2020]. Available from: https://nipy.org/nibabel/coordinate\_systems.html

\bibitem{brain-image}
ABDELKHALEK B. Segmentation of Cerebrospinal Fluid from 3D CT Brain Scans Using Modified Fuzzy C-Means Based on Super-Voxels. \textit{Annals of Computer Science and Information Systems} [online]. 2015, 5, pp. 809-818. [Accessed 20 April 2020]. ISSN 2300-5963. Available from: doi: 10.13140/RG.2.1.4733.0640

\bibitem{lecun1999}
LECUN Y., HAFFNER P., BOTTOU L., BENGIO Y. Object Recognition with Gradient-Based Learning. In: FORSYTH D.A., MUNDY J.L., GESÚ V. di, CIPOLLA R. \textit{Lecture Notes in Computer Science} [online]. Springer, 1999, pp. 319-345. [Accessed 30 April 2020]. Available at: http://yann.lecun.com/exdb/publis/pdf/lecun-99.pdf

\bibitem{alexnet2012}
KRIZHEVSKY A., SUTSKAVER I., HINTON G.E. ImageNet Classification with Deep Convolutional Neural Networks. \textit{NIPS} [online]. New York: Curran Associates Inc., 2012. [Accessed 1 May 2020]. Available from: https://papers.nips.cc/paper/4824-imagenet-classification-with-deep-convolutional-neural-networks.pdf

\bibitem{unet2015}
RONNEBERGER O., FISCHER P., BROX T. U-Net: Convolutional Networks for Biomedical Image Segmentation. In: \textit{Medical Image Computing and Computer-Assisted Intervention – MICCAI 2015} [online]. Cham: Springer, 2015. [Accessed 1 May 2020]. Available from: https://arxiv.org/pdf/1505.04597.pdf 

\bibitem{resnet2016}
HE K., ZHANG X., SUN J. Deep Residual Learning for Image Recognition. In: \textit{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)} [online]. Las Vegas: IEEE, 2016. [Accessed 2 May 2020]. Available from: https://www.cv-foundation.org/openaccess/content\_cvpr\_2016/papers/
He\_Deep\_Residual\_Learning\_CVPR\_2016\_paper.pdf

\bibitem{densenet2017}
HUANGG., LIU Z., VAN DER MAATEN L., WEINBERGER K. Q. Densely Connected Convolutional Networks. In: \textit{2017 IEEE Conference on Computer Vision and Pattern Recognition (CVPR)} [online]. Honolulu: IEEE, 2017. [Accessed 2 May 2020]. Available from: https://arxiv.org/pdf/1608.06993.pdf

\bibitem{rcnn2014}
GIRSHICK R., DONAHUE J. DARRELL T., MALIK J. Rich Feature Hierarchies for Accurate Object Detection and Semantic Segmentation. In: \textit{2014 IEEE Conference on Computer Vision and Pattern Recognition (CVPR)} [online]. Columbus: IEEE, 2014. [Accessed May 3 2020]. Available from: https://arxiv.org/pdf/1311.2524.pdf

\bibitem{fast-rcnn2015}
GIRSHICK R. Fast R-CNN. In: \textit{2015 IEEE International Conference on Computer Vision (ICCV)} [online]. Santiago: IEEE, 2015. [Accessed May 3 2020]. Available from: https://arxiv.org/pdf/1504.08083.pdf

\bibitem{faster-rcnn2017}
REN S., HE K., GIRSHICK R., SUN J. Faster R-CNN: Towards Real-Time Object Detection with Region Proposal Networks. \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence} [online]. 2017, 39(6), pp. 1137-1149. [Accessed 3 May 2020]. ISSN 1939-3539. Available from: https://arxiv.org/pdf/1506.01497.pdf

\bibitem{capsnet2017}
SABOUR S., FROSST N., HINTON G. Dynamic Routing between Capsules. In: {Proceedings of the 31st International Conference on Neural Information Processing Systems} [online]. Long Beach: Vurran Associates Inc., 2017. [Accessed May 4 2020]. Available from: https://arxiv.org/pdf/1710.09829.pdf

\bibitem{keras}
CHOLLET F et al. \textit{Keras}. 2015. Available from: https://keras.io

\bibitem{tensorflow}
ABADI M et al. \textit{TensorFlow: Large-Scale Machine Learning on Heterogeneous Systems}. 2015. Available from: https://www.tensorflow.org/

\bibitem{verse1}
LÖFFLER M. et al. A Vertebral Segmentation Dataset with Fracture Grading. \textit{Radiology: Artificial Intelligence (In Press)}. 2020.

\bibitem{verse2}
SEKUBOYINA A. et al. \textit{VerSe: A Vertebrae Labelling and Segmentation Benchmark}. 2020. Available from: arXiv:2001.09193

\bibitem{nibabel}
BRETT M. et al. \textit{NiBabel}. 2020. [Accessed June 4 2020]. Available from: doi: doi.org/10.5281/zenodo.3757992

\bibitem{nipype}
GORGOLEWSKI K. et al. Nipype: a flexible, lightweight and extensible neuroimaging data processing framework in Python. \textit{Frontiers in Neuroinformatics} [online]. 2011. [Accessed June 4 2020]. 5, p.13. ISSN: 1662-5196. Available from: doi: 10.3389/fninf.2011.00013   

\bibitem{jocic}
JOCIĆ M., \textit{Deep Learning Tutorial for Kaggle Ultrasound Nerve Segmentation competition, using Keras} [GitHub Repository]. 2017. Available from: https://github.com/jocicmarko/ultrasound-nerve-segmentation

\end{thebibliography}